Exploring probability distributions for bivariate temporal granularities

### 2019-12-15 main.Rmd
update name of subsections

## Estimation of the measured variable

@@

The grammar of graphics introduced a framework to incorporate underlying features for statistical graphics to construct them by relating data space to the graphic space [@Wilkinson1999-nk]. 
The layered grammar of graphics proposed by [@Wickham2009-pk], which is a modification over the former, suggests that graphics are made up of distinct layers of grammatical elements and meaningful plots are built around appropriate aesthetic mappings. 
<!-- seven grammatical elements in total, out of them three are essential.  -->

Briefly, the layered grammar defines the components of plot as:

@@

- **Facet**ting is a mechanism for splitting the data into subsets, then plotting each subset in a different panel. This is a powerful tool for exploratory data analysis as we can rapidly compare patterns in different parts of the data and can see whether they are the same or different.

@@

- Data: <$A_i$, $B_j(s)$, $v(s)$> $i \in {1, 2, \dots, n}$
- Aesthetic mapping: $A_i$ mapped to $x$ position and $v(s)$ to $y$ position
- Statistical transformation: Any descriptive or smoothing statistics that summarizes distribution
- Geometric objects: e.g. boxplot, letter value, violin, ridge, highest density regions

After the essential layers, the next layer being used is the facet which dictates how to split up our plot.

- Facet:  $B_j(s)$

@@

Different distribution plots might be appropriate depending on which features of the distrbution we are interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization. While we accomplish that, we need to bear in mind that any customized species of visualization might be constructed by varying the set of mappings between data properties and visual attributes such as position, shape and color. We are trying to address problems where even with good aesthetic qualities and good data, the graph might be confusing or misleading because of how people process the information.

@@

## Choice of exploratory visualization tool

>>>>

## Summarizing properties of the distribution

@@

The grammar of graphics introduced a framework to incorporate underlying features for statistical graphics to construct them by relating data space to the graphic space [@Wilkinson1999-nk]. 
The layered grammar of graphics proposed by [@Wickham2009-pk], which is a modification over the former, suggests that graphics are made up of distinct layers of grammatical elements. Briefly, the grammatical elements of any plot are as follows:

@@

- **Facet** dictates how to split up our plot and is a powerful tool for exploratory data analysis as we can rapidly compare patterns in different parts of the data and can see whether they are the same or different.

@@

- Data: <$A_i$, $B_j(s)$, $v(s)$> $i \in {1, 2, \dots, n}$
- Aesthetic mapping: $A_i$ mapped to $x$ position and $v(s)$ to $y$ position
- Statistical transformation: Any descriptive or smoothing statistics that summarizes distribution
- Geometric objects: examples can include boxplot, letter value, violin, ridge, highest density region plots
- Facet:  $B_j(s)$

@@

Hence, the ingredients for the plots are subsets of numbers (or categorical measurements), and the choice of faceting or axis alignment for the subset strata. The basic plot choice is display of density. Different plots might be appropriate depending on which features of the density we are interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization. While we accomplish that, we need to bear in mind that any customized species of visualization might be constructed by varying the set of mappings between data properties and visual attributes such as position, shape and color. We are trying to address problems where even with good aesthetic qualities and good data, the graph might be confusing or misleading because of how people process the information.

@@

## Choice of
